%!TEX root = ../Thesis.tex
\vspace*{20mm}
\noindent {\huge \textit{Publications during enrolment}}
\vspace{10mm}

\textbf{Arnatkevi\u{c}i\={u}t\.{e} A}, Fulcher BD, Fornito A. A practical guide to linking brain-wide gene expression and neuroimaging data. \textit{NeuroImage} (2019), 189, 353-367. \url{https://doi.org/10.1016/j.neuroimage.2019.01.011}.

Fornito A, \textbf{Arnatkevi\u{c}i\={u}t\.{e} A}, Fulcher, BD. Bridging the Gap between Connectome and Transcriptome. \textit{Trends in Cognitive Sciences} (2019), 23(1), 34-50. \url{https://doi:10.1016/j.tics.2018.10.005}.

\textbf{Arnatkevi\u{c}i\={u}t\.{e} A}*, Fulcher BD*, Pocock R, Fornito A. Hub connectivity, neuronal diversity, and gene expression in the Caenorhabditis elegans connectome. \textit{PLOS Computational Biology} (2018), 14(2): e1005989. \url{https://doi.org/10.1371/journal.pcbi.1005989}. * These authors contributed equally.

Hawi Z, Yates H, Pinar A, \textbf{Arnatkevi\u{c}i\={u}t\.{e} A}, Johnson B, Tong J, Pugsley K, Dark C, Pauper M, Klein M, Heussler H, Hiscock H, Fornito A, Tiego J, Finlay A, Vance A, Gill M, Kent L, Bellgrove M. A case-control genome-wide association study of ADHD discovers a novel association with the tenascin R (TNR) gene. \textit{Translational Psychiatry} (2018), 8, Article number: 284; \url{https://doi:10.1038/s41398-018-0329-x}.

Griksiene R, Monciunskaite R, \textbf{Arnatkevi\u{c}i\={u}t\.{e} A}, Ruksenas O. Does the use of hormonal contraceptives affect the mental rotation performance? \textit{Hormones and Behavior} (2018), 100, 29-38. \url{https://10.1016/j.yhbeh.2018.03.004}.

\subsection*{In submission}

\textbf{Arnatkevi\u{c}i\={u}t\.{e} A}, Fulcher BD, Fornito A. Uncovering the transcriptional signatures of hub connectivity in neural networks. In submission at \textit{Frontiers in Neural Circuits} (2018). Available at: \url{https://psyarxiv.com/7j4s2/}.
 
Oldham S, Fulcher BD, Parkes L, \textbf{Arnatkevi\u{c}i\={u}t\.{e} A}, Suo C, Fornito A. Consistency and differences between centrality measures across distinct classes of networks. In submission (2018). Available at: \url{https://arxiv.org/abs/1805.02375}.

Griksiene R, \textbf{Arnatkevi\u{c}i\={u}t\.{e} A}, Ruksenas O, Monciunskaite R, Koenig T, Mental rotation of sequentially presented 3D figures: sex and sex hormones related differences in behavioral and ERP measures. In submission (2018). 

\vspace{3mm}

